A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-02 mt-marathon.2013/PBML_article.tex
script to replace numbers with placeholder. /Achim Ruopp

The built-in feature functions in the phrase-based models are:

\begin{itemize}
  \item Translation model
  \item Language model
  \item Distortion model
  \item Lexicalized reordering model
  \item Word penalty
  \item Unknown word penalty
\end{itemize}

@@

Sparse features contain scores that may only be present occasionally. Also, there may be many more sparse features than dense features. There are typically 12 scores in a standard phrase-based model and 8 scores in a hierarchical phrase-based model. There may be millions of sparse score in a system with sparse features. However, only a few will be present in a particular hypothesis.

@@

\subsection{Moses}
Moses explicitly implements both dense and sparse features, and each score must be identifiable as one or the other.
The intuition behind this is that most systems will still contain dense features. Therefore, it would be more efficient to use dedicated dense vectors for these scores.

@@

\subsection{CDEC}
CDEC eschew the dense and sparse hybrid approach and implement only sparse maps. Dense features can still be modelled in the framework, with some loss of efficiency.

To improve speed and memory usage, hypotheses only store deltas of sparse features differences with antecedent hypotheses.

\subsection{Joshua}
As with CDEC, Joshua only supports sparse features, however, it uses a different tack to improve efficiency.

@@

\section*{Acknowledgements}
This research is supported by \ldots

>>>>

The built-in feature functions in the phrase-based models are:
\begin{itemize}
  \item Translation model
  \item Language model
  \item Distortion model
  \item Lexicalized reordering model
  \item Word penalty
  \item Unknown word penalty
\end{itemize}

@@

Sparse features contain scores that may only be present occasionally. Also, there may be many more sparse features than dense features. There are typically 14 scores from five feature functions in a standard phrase-based model and 7 scores in a hierarchical phrase-based model. There may be millions of sparse score in a system with sparse features. However, only a few will be present in a particular hypothesis.

@@

\subsection{Moses}
Moses explicitly implements both dense and sparse features. Each score must be identifiable as one or the other.
The intuition behind this is that most systems will still contain dense features. Therefore, it would be more efficient to use dedicated dense vectors for these scores.

@@

\subsection{CDEC}
CDEC eschew the dense and sparse hybrid approach and implement only sparse maps. Dense features can still be modelled in the framework with sparse features, with some loss of efficiency.

To improve speed and memory usage, hypotheses only store deltas of feature differences with antecedent hypotheses.

\subsection{Joshua}
As with CDEC, Joshua only supports sparse features, however, it uses a different strategy to improve efficiency.

@@

\section*{Acknowledgements}

The research leading to these results has received funding from the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement 288487 (MosesCore).
